IPv6 over Low-Power Wireless Personal Area Networks\\ MSc. Thesis Proposal

### 2009-12-18 trunk/doc/msc-proposal/msc-nd.tex
proposal: ND options

A NR message includes a 6LoWPAN  Address Option, described in Section \ref{nd.option.address}, for each address the host wants to bind for the interface, and a NC message may carry a 6LoWPAN Information Option, described in Section \ref{nd.option.info}, containing information about the prefixes of the LoWPAN along with other context information.

@@

\subsection{Message Options}
\subsubsection{6LoWPAN Address Option}\label{nd.option.address}

\subsubsection{6LoWPAN Information Option}\label{nd.option.info}

\subsubsection{6LoWPAN Summary Option}\label{nd.option.summary}

\subsubsection{Owner Interface Identifier Option}\label{sec:nd.oiio}

>>>>

A NR message includes a 6LoWPAN  Address Option, described in Section \ref{nd.option.address}, for each address the host wants to bind for the interface, and a NC message may carry a 6LoWPAN Information Option, described in Section \ref{nd.option.info}.

@@

\subsection{Message Options}
The 6LoWPAN-ND introduces four new message options described in this section.

\subsubsection{6LoWPAN Address Option}\label{nd.option.address}
The 6LoWPAN Address Option (6AO) is used in NR and NC messages to indicate the address which a node wants to register with an ER and to get the result of registration back. A NR/NC message can include multiple Address Options. The fields of the option allow to indicate the success or failure of the binding in an NC, as well as to compress the carried IPv6 address to different extent.

\subsubsection{6LoWPAN Information Option}\label{nd.option.info}
The 6LoWPAN Information Option (6IO) is used to carry prefix information. A RA message includes one Information Option for each listed prefix.  The option also allows to disseminate contexts used in 6LoWPAN address compression and identified by a Context Identifier (CID).

\subsubsection{6LoWPAN Summary Option}\label{nd.option.summary}
The 6LoWPAN Summary Option (6SO) associates the current prefix options with a sequence number. It allows prefix options themselves to be sent only periodically in unsolicited RAs, reducing the message size. When the sequence number of this option has a new value, then the prefix information has likely changed, and, in this case, a node requests the prefix information with an RS. An RA sent in response to a unicast RS always includes the full set of prefix information.

\subsubsection{Owner Interface Identifier Option}\label{sec:nd.oiio}
The Owner Interface Identifier Option (OIIO) is used with classic NS and NA messages between ERs over a backbone link to identify bindings and whiteboard entries.
